---
title:  |
  | Your report
author: 
- "You, [VIB - Nucleomics Core, nucleomics@vib.be]"
date: $`r format(Sys.time(), "%a %b %d, %Y")`$ - version 1.0
fontsize: 10pt
geometry: top=1cm, bottom=1cm, left=2.5cm, right=1.5cm, includeheadfoot=true
bibliography: tex_data/bibliography.bib
output:
  rmarkdown::pdf_document:
    toc: true
    toc_depth: 3
    number_sections: false
    fig_caption: false
    fig_width: 5
    fig_height: 5
    includes:  
      in_header: tex_data/preamble.tex
editor_options: 
  chunk_output_type: console
---

```{r setup, eval=TRUE, include=FALSE, echo=FALSE}

# set default parameters [echo=TRUE to include code]
# general
library("knitr")
library("ggplot2")
library("RColorBrewer")
# any package you need here

# edit next line to point to your current report path
workdir <- "/data/analyses/Rmd-report_template"
opts_chunk$set(message=FALSE, 
               warning=FALSE, 
               eval=FALSE,
               echo=FALSE,
               include=TRUE,
               fig.cap="",
               fig.show="asis",
               fig.keep="high",
               cache=TRUE,
               comment=NA,
               root.dir=workdir)
options(scipen=999)
setwd(workdir)

# some key default options here
# eval=FALSE by default unless you set your block to TRUE
# echo=FALSE by default (do not show the code) unless you change it to TRUE
# include=TRUE by default unless you set it to FALSE in your block
# 
# many other options can be tuned as documented by *Yihui Xie* at **[Knitr home page](https://yihui.org/knitr/)**

```

\bigskip

\footnotesize

last edits: $`r format(Sys.time(), "%a %b %d, %Y")`$

\normalsize

\bigskip

\bigskip

# Aim

Add a report picture to put on top of page1 by editing the **tex_data/preamble.tex** file (also add latex goodies here)

Look for references and get them formatted for you with **[texmed](http://www.bioinformatics.org/texmed/)**

Use the bibtex formatted references added to **tex_data/bibliography.bib** like this Samtools example [@pmid19505943] to show references inline.

Show some text in smaller fonts

\footnotesize

```
Lorem Ipsum is simply dummy text of the printing and typesetting industry. 
Lorem Ipsum has been the industry's standard dummy text ever since the 1500s, 
when an unknown printer took a galley of type and scrambled it to make a type specimen book. 
It has survived not only five centuries, but also the leap into electronic typesetting, 
remaining essentially unchanged. It was popularised in the 1960s with the release of 
Letraset sheets containing Lorem Ipsum passages, and more recently with desktop publishing 
software like Aldus PageMaker including versions of Lorem Ipsum.
```

\normalsize


Insert a markdown table prepared from an excel copy-paste at **[tablesgenerator](https://www.tablesgenerator.com/)**

\footnotesize

| Tables   |      Are      |  Cool |
|----------|:-------------:|------:|
| col 1 is |  left-aligned | $1600 |
| col 2 is |    centered   |   $12 |
| col 3 is | right-aligned |    $1 |

\normalsize

Insert a picture and control its size from a file stored in the local **pictures/** folder.


\begin{center}

\includegraphics[width=150pt]{pictures/knit-logo.png}

\end{center}

Inset code blocks (hint! can be bash, python, R, others)

\footnotesize

```{bash test, echo=TRUE, eval=TRUE}
# this code will be shown in the report AND run
echo "hello world!"
```

\bigskip

```{bash test2, echo=TRUE, eval=FALSE}
# this code will be shown in the report BUT NOT run due to eval=FALSE
echo "shown inline BUT not run!"
```

\normalsize

# Conclusion

Bla Bla

\bigskip

\footnotesize

last edits: $`r format(Sys.time(), "%a %b %d, %Y")`$

\normalsize

\footnotesize

```{r, eval=FALSE, echo=FALSE}
sessionInfo()
```

\newpage
 
# References

\bigskip
 
\footnotesize
 
 